---
title: "{{PROJECT_NAME}} - Small Variants Quality Control Report"
subtitle: "{{GENE_NAME}} Gene Analysis"
author: "{{PROJECT_AUTHOR}} ({{PROJECT_CODE}})"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
    self-contained: true
    self-contained-math: true
    keep-md: false
    fig-width: 10
    fig-height: 6
execute:
  echo: false
  warning: false
  message: false
lightbox:
  match: auto
  effect: zoom
  desc-position: bottom
  loop: true
---

```{r setup}
#| include: false
library(tidyverse)
library(knitr)
library(kableExtra)
library(DT)
library(plotly)
library(gt)

# Set global options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center")

# Define data directory
data_dir <- "data"

# Project information from pipeline
project_info <- list(
  code = "{{PROJECT_CODE}}",
  name = "{{PROJECT_NAME}}",
  author = "{{PROJECT_AUTHOR}}",
  gene = "{{GENE_NAME}}"
)
```

# Executive Summary

This report presents a detailed quality control analysis of small germline variants identified in the **{{GENE_NAME}}** 
gene as part of the **{{PROJECT_CODE}}** research initiative. The analysis includes comprehensive QC visualizations, 
basic and custom filtering strategies, and detailed statistical summaries of variant distributions and participant metadata.

Key components of this report include:

- Quality control visualizations of variant distributions and impact assessments
- Participant metadata analysis with demographic and clinical context
- Comprehensive filtering analysis with somatic/germline distinction
- Interactive tables for detailed variant exploration
- Statistical summaries of all analysis steps

---

# Raw Variants QC Analysis

## 1. Variant Distribution and Impact Assessment

This section presents visualizations of all raw variant quality control metrics, including impact distribution, 
minor allele frequencies, and density distributions across the {{GENE_NAME}} gene.

```{r qc-impact-frequency}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 6

# Display QC_IMPACT_Frequency plot
impact_plot_files <- list.files(data_dir, pattern = "*_QC_IMPACT_Frequency\\.pdf$", full.names = TRUE)

if (length(impact_plot_files) > 0) {
  pdf_path <- impact_plot_files[1]
  
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "qc_impact_frequency.png"
      png::writePNG(img, png_filename)
      
      cat('\n<div style="margin: 30px 0; text-align: center;">\n')
      cat('  <img src="', png_filename, '" style="width:90%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="IMPACT Frequency Distribution" />\n', sep = "")
      cat('</div>\n')
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', basename(pdf_path), '</p>\n')
      cat('</div>\n')
    })
  }
} else {
  cat("⚠️ QC IMPACT Frequency plot not found.\n")
}
```

**_Figure 1:_** *Distribution of variant consequences by IMPACT level (HIGH, MODERATE, LOW, MODIFIER) showing the functional 
significance of identified variants in {{GENE_NAME}}.*

```{r qc-maf-distribution}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 6

# Display QC_MAF_Distribution plot
maf_plot_files <- list.files(data_dir, pattern = "*_QC_MAF_Distribution\\.pdf$", full.names = TRUE)

if (length(maf_plot_files) > 0) {
  pdf_path <- maf_plot_files[1]
  
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "qc_maf_distribution.png"
      png::writePNG(img, png_filename)
      
      cat('\n<div style="margin: 30px 0; text-align: center;">\n')
      cat('  <img src="', png_filename, '" style="width:90%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="MAF Distribution" />\n', sep = "")
      cat('</div>\n')
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', basename(pdf_path), '</p>\n')
      cat('</div>\n')
    })
  }
} else {
  cat("⚠️ QC MAF Distribution plot not found.\n")
}
```

**_Figure 2:_** *Minor Allele Frequency (MAF) distribution showing the population frequency spectrum of variants 
identified in {{GENE_NAME}}, with emphasis on rare variants (MAF < 0.001).*

```{r qc-maf-vs-impact}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 6

# Display QC_MAFvsIMPACT plot
maf_impact_plot_files <- list.files(data_dir, pattern = "*_QC_MAFvsIMPACT\\.pdf$", full.names = TRUE)

if (length(maf_impact_plot_files) > 0) {
  pdf_path <- maf_impact_plot_files[1]
  
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "qc_maf_vs_impact.png"
      png::writePNG(img, png_filename)
      
      cat('\n<div style="margin: 30px 0; text-align: center;">\n')
      cat('  <img src="', png_filename, '" style="width:90%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="MAF vs IMPACT" />\n', sep = "")
      cat('</div>\n')
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', basename(pdf_path), '</p>\n')
      cat('</div>\n')
    })
  }
} else {
  cat("⚠️ QC MAF vs IMPACT plot not found.\n")
}
```

**_Figure 3:_** *Relationship between Minor Allele Frequency and variant impact, demonstrating the inverse correlation 
between population frequency and predicted functional consequence.*

```{r qc-density-variants}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 6

# Display QC_Density_variants plot
density_plot_files <- list.files(data_dir, pattern = "*_QC_Density_variants\\.pdf$", full.names = TRUE)

if (length(density_plot_files) > 0) {
  pdf_path <- density_plot_files[1]
  
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "qc_density_variants.png"
      png::writePNG(img, png_filename)
      
      cat('\n<div style="margin: 30px 0; text-align: center;">\n')
      cat('  <img src="', png_filename, '" style="width:90%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="Variant Density Distribution" />\n', sep = "")
      cat('</div>\n')
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', basename(pdf_path), '</p>\n')
      cat('</div>\n')
    })
  }
} else {
  cat("⚠️ QC Density variants plot not found.\n")
}
```

**_Figure 4:_** *Genomic distribution and density of variants across the {{GENE_NAME}} gene, highlighting regions 
with variant clustering and potential mutational hotspots.*

## 2. Participant Metadata Analysis

This section presents the demographic and clinical characteristics of participants with all raw variants in {{GENE_NAME}}, 
providing crucial context for variant interpretation and population analysis.

```{r qc-participant-metadata}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 6

# Look for the specific QC participant metadata file
metadata_file <- paste0(project_info$gene, "_QC_CanonicalVar_PartMetadata_Barplots.pdf")
pdf_path <- file.path(data_dir, metadata_file)

if (file.exists(pdf_path)) {
  # Convert PDF to PNG and display
  img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
  png_filename <- "qc_metadata_main.png"
  png::writePNG(img, png_filename)
  
  # Display the image
  cat('![](', png_filename, '){width="100%"}\n\n', sep = "")
  
} else {
  cat("⚠️ Participant metadata plot not found:", metadata_file, "\n")
}
```

**_Figure 5:_** *Distribution of participants by demographic and clinical characteristics, including age, sex, 
disease categories, and other relevant metadata for individuals carrying {{GENE_NAME}} variants. Click the image to view additional metadata plots (pathogenic, VUS, etc.) in the gallery.*

---

# Filtering Analysis

## 3. Basic Filtering

This section presents the results of basic filtering applied to the small variants dataset. Basic filtering includes 
standard quality thresholds, population frequency cutoffs, and canonical transcript selection criteria.

### 3.1 Basic Filtering Statistics

```{r basic-filter-stats-table}
#| echo: false

# Load basic filtering statistics
basic_stats_files <- list.files(data_dir, pattern = "*_small_variants_filter_basic_stats\\.csv$", full.names = TRUE)

if (length(basic_stats_files) > 0) {
  basic_stats <- read_csv(basic_stats_files[1], show_col_types = FALSE)
  
  if (nrow(basic_stats) > 0) {
    # Create a nicely formatted table using gt
    basic_stats %>%
      mutate(
        metric = case_when(
          metric == "total_raw_variants" ~ "Total Raw Variants",
          metric == "total_canonical_variants" ~ "Total Canonical Variants", 
          metric == "total_canonical_-" ~ "   • Canonical '-' Variants (No ClinVar)",
          metric == "total_canonical_benign" ~ "   • Canonical Benign Variants",
          metric == "total_canonical_pathogenic" ~ "   • Canonical Pathogenic Variants",
          metric == "total_canonical_VUS" ~ "   • Canonical VUS Variants",
          metric == "total_canonical_nonBenign" ~ "Canonical Non-Benign Variants",
          metric == "total_canonical_nonBenign_MAF<0.001" ~ "Canonical Non-Benign and MAF < 0.001 Variants",
          TRUE ~ metric
        )
      ) %>%
      gt() %>%
      tab_header(
        title = paste("Basic Filtering Statistics for", project_info$gene),
        subtitle = "Progressive filtering steps with variant counts and number of participants"
      ) %>%
      cols_label(
        metric = "Filtering Step",
        variant_count = "Variant Count",
        participant_count = "Participant Count"
      ) %>%
      tab_style(
        style = list(
          cell_fill(color = "#f8f9fa"),
          cell_text(weight = "bold")
        ),
        locations = cells_column_labels()
      ) %>%
      tab_style(
        style = list(
          cell_fill(color = "#e3f2fd"),
          cell_text(weight = "bold")
        ),
        locations = cells_body(rows = metric == "Final Filtered Variants (MAF<0.001)")
      ) %>%
      fmt_number(
        columns = c(variant_count, participant_count),
        decimals = 0
      )
  } else {
    cat("No basic filtering statistics data available.")
  }
} else {
  cat("No basic filtering statistics files found.")
}
```

**_Table 1:_** *Progressive filtering statistics showing the impact of each filtering step on variant and participant counts. 
The final row represents the high-quality variant set used for downstream analysis.*

### 3.2 Variant Filter QC

```{r basic-filter-variant-plots}
#| echo: false
#| results: asis
#| fig-width: 10
#| fig-height: 8

# Look for basic filtering plots - excluding participant metadata and lollipop plots
basic_filter_plot_files <- list.files(data_dir, pattern = ".*small_variants_filter_basic.*\\.pdf$", full.names = TRUE)

# If not found, try alternative patterns
if (length(basic_filter_plot_files) == 0) {
  basic_filter_plot_files <- list.files(data_dir, pattern = ".*filter_basic.*(somatic|germline|unknown).*\\.pdf$", full.names = TRUE)
  basic_filter_plot_files <- basic_filter_plot_files[grepl("small_variants", basic_filter_plot_files)]
}

# Exclude participant metadata and lollipop plots
basic_filter_plot_files <- basic_filter_plot_files[!grepl("PartMetadata|Lollipop", basic_filter_plot_files)]

if (length(basic_filter_plot_files) > 0) {
  cat('\n<!-- Basic filtering variant plots -->\n')
  
  # Define plot order for variant visualizations
  plot_order <- c("IMPACT_Frequency", "MAF_Distribution", "MAFvsIMPACT", "Density_variants")
  
  # Sort files by plot type for consistent ordering
  ordered_files <- c()
  for (plot_type in plot_order) {
    matching_files <- basic_filter_plot_files[grepl(plot_type, basic_filter_plot_files)]
    ordered_files <- c(ordered_files, matching_files)
  }
  
  # Add any remaining files not in the predefined order
  remaining_files <- setdiff(basic_filter_plot_files, ordered_files)
  ordered_files <- c(ordered_files, remaining_files)
  
  for (plot_idx in seq_along(ordered_files)) {
    pdf_path <- ordered_files[plot_idx]
    pdf_name <- basename(pdf_path)
    plot_name <- gsub("\\.(pdf)$", "", pdf_name)
    
    # Skip NoData placeholder files
    if (grepl("NoData", pdf_name)) next
    
    # Convert PDF to PNG
    if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
      tryCatch({
        img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
        png_filename <- paste0("basic_filter_variant_plot_", plot_idx, ".png")
        png::writePNG(img, png_filename)
        
        cat('\n<div style="margin: 30px 0; text-align: center;">\n')
        cat('  <img src="', png_filename, '" style="width:90%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="', plot_name, '" />\n', sep = "")
        cat('</div>\n')
        
      }, error = function(e) {
        cat('\n<div style="padding:15px; background:#fff3cd; border:1px solid #ffc107; border-radius:5px; margin:10px 0;">\n')
        cat('  <p style="color:#856404; margin:0;">Could not convert PDF: ', pdf_name, '</p>\n')
        cat('</div>\n')
      })
    }
  }
  
  cat('\n<!-- End basic filtering variant plots -->\n\n')
} else {
  cat("ℹ️ No basic filtering variant plot files found.\n")
}
```

**_Figure 6-9:_** *Variant distribution visualizations after basic filtering, showing impact assessments, MAF distributions, 
and genomic density patterns for high-quality variants in {{GENE_NAME}}.*

### 3.3 Lollipop Plots

```{r basic-filter-lollipop-plots}
#| echo: false
#| results: asis

# Look for basic filtering lollipop plots - ONLY pathogenic and VUS
lollipop_plot_files <- list.files(data_dir, pattern = ".*filter_basic.*Lollipop.*(pathogenic|VUS).*\\.pdf$", full.names = TRUE, ignore.case = TRUE)

if (length(lollipop_plot_files) > 0) {
  # Sort files to ensure pathogenic comes before VUS
  pathogenic_files <- lollipop_plot_files[grepl("pathogenic", lollipop_plot_files, ignore.case = TRUE)]
  vus_files <- lollipop_plot_files[grepl("VUS", lollipop_plot_files, ignore.case = TRUE)]
  lollipop_plot_files <- c(pathogenic_files, vus_files)
  
  # Generate unique lightbox group for basic filtering lollipops
  lightbox_group <- "basic-lollipop-gallery"
  
  # Display ONLY the first image (pathogenic), rest accessible via lightbox
  pdf_path <- lollipop_plot_files[1]
  pdf_name <- basename(pdf_path)
  
  # Convert first PDF to PNG and display
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "basic_lollipop_main.png"
      png::writePNG(img, png_filename)
      
      # Show first image without label in lightbox group
      cat('![](', png_filename, '){group="', lightbox_group, '" width="100%"}\n\n', sep = "")
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', pdf_name, '</p>\n')
      cat('</div>\n\n')
    })
  }
  
  # Process remaining PDFs but DON'T display them (only for lightbox)
  if (length(lollipop_plot_files) > 1) {
    for (pdf_idx in 2:length(lollipop_plot_files)) {
      pdf_path <- lollipop_plot_files[pdf_idx]
      pdf_name <- basename(pdf_path)
      
      # Convert PDF to PNG but don't display (hidden for lightbox only)
      if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
        tryCatch({
          img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
          png_filename <- paste0("basic_lollipop_", pdf_idx, ".png")
          png::writePNG(img, png_filename)
          
          # Add to lightbox group but hide from main view (without label)
          cat('![](', png_filename, '){group="', lightbox_group, '" style="display:none;"}\n\n', sep = "")
          
        }, error = function(e) {
          # Silent error for hidden images
        })
      }
    }
  }
  
  cat('\n**_Figure 9b:_** *Lollipop plots showing variant positions along the {{GENE_NAME}} protein structure for pathogenic and VUS variants after basic filtering. Click the image to toggle between variant categories.*\n\n')
} else {
  cat("ℹ️ No pathogenic or VUS lollipop plots found for basic filtering.\n\n")
}
```

### 3.4 Participant Metadata

```{r basic-filter-participant-metadata}
#| echo: false
#| results: asis

# Look for all basic filtering metadata plots including all variant types
metadata_plot_files <- list.files(data_dir, pattern = ".*filter_basic.*PartMetadata_Barplots.*\\.pdf$", full.names = TRUE)

if (length(metadata_plot_files) > 0) {
  # Sort files to ensure AllFiltered comes first
  allfiltered_file <- metadata_plot_files[grepl("AllFiltered", metadata_plot_files)]
  other_files <- metadata_plot_files[!grepl("AllFiltered", metadata_plot_files)]
  metadata_plot_files <- c(allfiltered_file, other_files)
  
  # Generate unique lightbox group for basic filtering
  lightbox_group <- "basic-metadata-gallery"
  
  # Display ONLY the first image (AllFiltered), rest accessible via lightbox
  pdf_path <- metadata_plot_files[1]
  pdf_name <- basename(pdf_path)
  
  # Convert first PDF to PNG and display
  if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
    tryCatch({
      img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
      png_filename <- "basic_metadata_main.png"
      png::writePNG(img, png_filename)
      
      # Show first image without label in lightbox group
      cat('![](', png_filename, '){group="', lightbox_group, '" width="100%"}\n\n', sep = "")
      
    }, error = function(e) {
      cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
      cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', pdf_name, '</p>\n')
      cat('</div>\n\n')
    })
  }
  
  # Process remaining PDFs but DON'T display them (only for lightbox)
  if (length(metadata_plot_files) > 1) {
    for (pdf_idx in 2:length(metadata_plot_files)) {
      pdf_path <- metadata_plot_files[pdf_idx]
      pdf_name <- basename(pdf_path)
      
      # Convert PDF to PNG but don't display (hidden for lightbox only)
      if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
        tryCatch({
          img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
          png_filename <- paste0("basic_metadata_", pdf_idx, ".png")
          png::writePNG(img, png_filename)
          
          # Add to lightbox group but hide from main view (without label)
          cat('![](', png_filename, '){group="', lightbox_group, '" style="display:none;"}\n\n', sep = "")
          
        }, error = function(e) {
          # Silent error for hidden images
        })
      }
    }
  }
} else {
  cat("Participant metadata plots not found for basic filtering.\n")
}
```

**_Figure 10:_** *Distribution of participants carrying basic-filtered variants by demographic and clinical characteristics, 
providing context for the filtered {{GENE_NAME}} variant set. Click the image to view additional metadata plots (pathogenic, VUS, etc.) in the gallery.*

### 3.4 Filtered Variants Table

```{r basic-filtered-variants-table}
#| echo: false

# Load basic filtered variants for interactive table
basic_filtered_files <- list.files(data_dir, pattern = "*_small_variants_filter_basic_filtered\\.rds$", full.names = TRUE)

if (length(basic_filtered_files) > 0) {
  basic_filtered_data <- map_dfr(basic_filtered_files, ~{
    data <- readRDS(.x)
    if (is.data.frame(data) && nrow(data) > 0) {
      data
    } else {
      NULL 
    }
  })
  
  if (!is.null(basic_filtered_data) && nrow(basic_filtered_data) > 0) {
    # Select specific columns for display in the requested order
    display_cols <- c(
      "LabelVarPlot", "POS_variant", "REF_variant", "ALT_variant", 
      "IMPACT_annotation", "Existing_variation_annotation", "Consequence_annotation", 
      "MAX_AF_annotation", "CLIN_SIG_annotation", "NS_variant"
    )
    
    # Filter to available columns
    available_cols <- intersect(display_cols, names(basic_filtered_data))
    
    # Create interactive table with download buttons
    dt_table <- basic_filtered_data %>%
      select(any_of(available_cols)) %>%
      datatable(
        caption = paste("Basic Filtered Variants for", project_info$gene),
        filter = 'top',
        extensions = c('Buttons'),
        options = list(
          pageLength = 10,
          scrollX = TRUE,
          autoWidth = TRUE,
          columnDefs = list(
            list(className = 'dt-center', targets = '_all')
          ),
          dom = 'Bfrtip',
          buttons = list(
            'copy',
            list(extend = 'csv', filename = paste0(project_info$gene, '_basic_filtered_variants')),
            list(extend = 'excel', filename = paste0(project_info$gene, '_basic_filtered_variants')),
            list(extend = 'pdf', filename = paste0(project_info$gene, '_basic_filtered_variants'))
          )
        ),
        rownames = FALSE,
        class = 'cell-border stripe hover'
      )
    
    # Only apply IMPACT formatting if the column exists
    if ("IMPACT_annotation" %in% available_cols) {
      dt_table <- dt_table %>%
        formatStyle(
          'IMPACT_annotation',
          backgroundColor = styleEqual(
            c('HIGH', 'MODERATE', 'LOW', 'MODIFIER'),
            c('#ffcccc', '#ffffcc', '#ccffcc', '#e6e6e6')
          )
        )
    }
    
    dt_table
  } else {
    cat("No basic filtered variant data available.")
  }
} else {
  cat("No basic filtered variants RDS files found.")
}
```

**_Table 2:_** *Interactive table of variants that passed basic filtering criteria for {{GENE_NAME}}. 
These represent high-quality, rare variants (MAF < 0.001) from canonical transcripts, excluding benign variants. 
Use the search and filter features to explore specific variants of interest.*

---

## 4. Custom Filtering Results

```{r custom-filters-detection}
#| echo: false

# Detect custom filters by looking for non-basic filter files
all_filter_stats <- list.files(data_dir, pattern = ".*small_variants_filter_.*_stats\\.csv$", full.names = TRUE)
custom_filter_stats <- all_filter_stats[!grepl("filter_basic", all_filter_stats)]

# Extract unique custom filter names with more flexible pattern
custom_filter_names <- c()
for (file in custom_filter_stats) {
  # Extract filter name from filename pattern: {gene}_small_variants_{filter_type}_stats.csv
  filter_match <- str_extract(basename(file), "filter_[^_]+")
  if (!is.na(filter_match) && filter_match != "filter_basic") {
    custom_filter_names <- c(custom_filter_names, filter_match)
  }
}
custom_filter_names <- unique(custom_filter_names)
```

```{r custom-filters-sections, results='asis'}
#| echo: false

if (length(custom_filter_names) > 0) {
  for (filter_name in custom_filter_names) {
    # Clean filter name for display
    filter_display <- str_replace_all(filter_name, "_", " ") %>% str_to_title()
    
    # Main filter section (### level 3)
    cat('\n### 4.', match(filter_name, custom_filter_names), ' ', filter_display, '\n\n', sep = "")
    
    # Statistics subsection (#### level 4)
    cat('\n#### 4.', match(filter_name, custom_filter_names), '.1 ', filter_display, ' Statistics\n\n', sep = "")
    
    # Stats table for this custom filter
    custom_stats_file <- list.files(data_dir, pattern = paste0(".*", filter_name, "_stats\\.csv$"), full.names = TRUE)
    
    if (length(custom_stats_file) > 0) {
      custom_stats <- read_csv(custom_stats_file[1], show_col_types = FALSE)
      
      if (nrow(custom_stats) > 0) {
        stats_table <- custom_stats %>%
          filter(grepl(paste0(filter_name, "_after_custom_filtering"), metric)) %>%
          mutate(
            metric = paste("Final", filter_display, "Variants")
          ) %>%
          gt() %>%
          tab_header(
            title = paste(filter_display, "Filtering Statistics"),
            subtitle = paste("Custom filtering results for", project_info$gene)
          ) %>%
          cols_label(
            metric = "Filtering Step",
            variant_count = "Variant Count", 
            participant_count = "Participant Count"
          ) %>%
          fmt_number(
            columns = c(variant_count, participant_count),
            decimals = 0
          )
        
        print(stats_table)
      }
    }
    
    cat('\n**_Table ', 2 + match(filter_name, custom_filter_names), ':_** ', filter_display, ' filtering statistics showing variant and participant counts at each filtering stage.\n\n', sep = "")
    
    # Variant Filter QC subsection (#### level 4)
    cat('\n#### 4.', match(filter_name, custom_filter_names), '.2 Variant Filter QC\n\n', sep = "")
    
    custom_plot_files <- list.files(data_dir, pattern = paste0(".*small_variants_", filter_name, ".*(somatic|germline|unknown).*\\.pdf$"), full.names = TRUE)
    
    if (length(custom_plot_files) == 0) {
      custom_plot_files <- list.files(data_dir, pattern = paste0(".*", filter_name, ".*\\.pdf$"), full.names = TRUE)
    }
    
    variant_plot_files <- custom_plot_files[!grepl("PartMetadata|Lollipop", custom_plot_files)]
    
    if (length(variant_plot_files) > 0) {
      plot_counter <- 1
      for (pdf_path in variant_plot_files) {
        pdf_name <- basename(pdf_path)
        
        if (grepl("NoData", pdf_name)) next
        
        if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
          tryCatch({
            img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
            png_filename <- paste0("custom_", filter_name, "_variant_plot_", plot_counter, ".png")
            png::writePNG(img, png_filename)
            
            cat('\n<div style="margin: 20px 0; text-align: center;">\n')
            cat('  <img src="', png_filename, '" style="width:85%; height:auto; border:1px solid #dee2e6; border-radius:4px; box-shadow: 0 2px 4px rgba(0,0,0,0.1);" alt="', pdf_name, '" />\n', sep = "")
            cat('</div>\n')
            
            plot_counter <- plot_counter + 1
          }, error = function(e) {
            # Skip silently
          })
        }
      }
      
      cat('\n**_Figure ', 10 + match(filter_name, custom_filter_names), ':_** *Variant distribution visualizations after ', filter_display, ', showing impact assessments and genomic patterns for {{GENE_NAME}}.*\n\n', sep = "")
    } else {
      cat('\nNo variant QC plots found for ', filter_display, '.\n\n', sep = "")
    }
    
    # Lollipop Plots subsection (#### level 4)
    cat('\n#### 4.', match(filter_name, custom_filter_names), '.3 Lollipop Plots\n\n', sep = "")
    
    lollipop_plot_files <- list.files(data_dir, pattern = paste0(".*", filter_name, ".*Lollipop.*\\.pdf$"), full.names = TRUE)
    
    if (length(lollipop_plot_files) > 0) {
      allfiltered_file <- lollipop_plot_files[grepl("AllFiltered", lollipop_plot_files)]
      other_files <- lollipop_plot_files[!grepl("AllFiltered", lollipop_plot_files)]
      lollipop_plot_files <- c(allfiltered_file, other_files)
      
      lightbox_group <- paste0("custom-", filter_name, "-lollipop-gallery")
      
      pdf_path <- lollipop_plot_files[1]
      pdf_name <- basename(pdf_path)
      
      if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
        tryCatch({
          img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
          png_filename <- paste0("custom_", filter_name, "_lollipop_main.png")
          png::writePNG(img, png_filename)
          
          cat('![](', png_filename, '){group="', lightbox_group, '" width="100%"}\n\n', sep = "")
          
        }, error = function(e) {
          cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
          cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', pdf_name, '</p>\n')
          cat('</div>\n\n')
        })
      }
      
      if (length(lollipop_plot_files) > 1) {
        for (pdf_idx in 2:length(lollipop_plot_files)) {
          pdf_path <- lollipop_plot_files[pdf_idx]
          
          if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
            tryCatch({
              img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
              png_filename <- paste0("custom_", filter_name, "_lollipop_", pdf_idx, ".png")
              png::writePNG(img, png_filename)
              
              cat('![](', png_filename, '){group="', lightbox_group, '" style="display:none;"}\n\n', sep = "")
              
            }, error = function(e) {
              # Silent
            })
          }
        }
      }
      
      cat('\n**_Figure ', 10 + length(custom_filter_names) + match(filter_name, custom_filter_names), 'b:_** *Lollipop plots showing variant positions along the {{GENE_NAME}} protein structure after ', filter_display, '. Click the image to view additional variant categories in the gallery.*\n\n', sep = "")
    } else {
      cat('\nNo lollipop plots found for ', filter_display, '.\n\n', sep = "")
    }
    
    # Participant Metadata subsection (#### level 4)
    cat('\n#### 4.', match(filter_name, custom_filter_names), '.4 Participant Metadata\n\n', sep = "")
    
    metadata_plot_files <- list.files(data_dir, pattern = paste0(".*", filter_name, ".*PartMetadata_Barplots.*\\.pdf$"), full.names = TRUE)
    
    if (length(metadata_plot_files) > 0) {
      allfiltered_file <- metadata_plot_files[grepl("AllFiltered", metadata_plot_files)]
      other_files <- metadata_plot_files[!grepl("AllFiltered", metadata_plot_files)]
      metadata_plot_files <- c(allfiltered_file, other_files)
      
      lightbox_group <- paste0("custom-", filter_name, "-metadata-gallery")
      
      pdf_path <- metadata_plot_files[1]
      pdf_name <- basename(pdf_path)
      
      if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
        tryCatch({
          img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
          png_filename <- paste0("custom_", filter_name, "_metadata_main.png")
          png::writePNG(img, png_filename)
          
          cat('![](', png_filename, '){group="', lightbox_group, '" width="100%"}\n\n', sep = "")
          
        }, error = function(e) {
          cat('\n<div style="padding:20px; background:#f8d7da; border:1px solid #f5c2c7; border-radius:5px;">\n')
          cat('  <p style="color:#842029; margin:0;">Could not convert PDF: ', pdf_name, '</p>\n')
          cat('</div>\n\n')
        })
      }
      
      if (length(metadata_plot_files) > 1) {
        for (pdf_idx in 2:length(metadata_plot_files)) {
          pdf_path <- metadata_plot_files[pdf_idx]
          
          if (requireNamespace("pdftools", quietly = TRUE) && requireNamespace("png", quietly = TRUE)) {
            tryCatch({
              img <- pdftools::pdf_render_page(pdf_path, page = 1, dpi = 300)
              png_filename <- paste0("custom_", filter_name, "_metadata_", pdf_idx, ".png")
              png::writePNG(img, png_filename)
              
              cat('![](', png_filename, '){group="', lightbox_group, '" style="display:none;"}\n\n', sep = "")
              
            }, error = function(e) {
              # Silent
            })
          }
        }
      }
      
      cat('\n**_Figure ', 10 + 2*length(custom_filter_names) + match(filter_name, custom_filter_names), ':_** *Distribution of participants carrying ', filter_display, ' variants by demographic and clinical characteristics. Click the image to view additional metadata plots in the gallery.*\n\n', sep = "")
    } else {
      cat('\nNo participant metadata plots found for ', filter_display, '.\n\n', sep = "")
    }
    
    # Filtered Variants Table subsection (#### level 4)
    cat('\n#### 4.', match(filter_name, custom_filter_names), '.5 Filtered Variants Table\n\n', sep = "")
    
    custom_filtered_files <- list.files(data_dir, pattern = paste0(".*", filter_name, "_filtered\\.rds$"), full.names = TRUE)
    
    if (length(custom_filtered_files) > 0) {
      tryCatch({
        custom_filtered_data <- readRDS(custom_filtered_files[1])
        
        if (is.data.frame(custom_filtered_data) && nrow(custom_filtered_data) > 0) {
          display_cols <- c(
            "LabelVarPlot", "POS_variant", "REF_variant", "ALT_variant", 
            "IMPACT_annotation", "Existing_variation_annotation", "Consequence_annotation", 
            "MAX_AF_annotation", "CLIN_SIG_annotation", "NS_variant"
          )
          
          available_cols <- intersect(display_cols, names(custom_filtered_data))
          
          dt_table <- custom_filtered_data %>%
            select(any_of(available_cols)) %>%
            datatable(
              caption = paste(filter_display, "Filtered Variants for", project_info$gene),
              filter = "top",
              extensions = c('Buttons'),
              options = list(
                pageLength = 10, 
                scrollX = TRUE, 
                autoWidth = TRUE,
                columnDefs = list(
                  list(className = 'dt-center', targets = '_all')
                ),
                dom = 'Bfrtip',
                buttons = list(
                  'copy',
                  list(extend = 'csv', filename = paste0(project_info$gene, '_', filter_name, '_filtered_variants')),
                  list(extend = 'excel', filename = paste0(project_info$gene, '_', filter_name, '_filtered_variants')),
                  list(extend = 'pdf', filename = paste0(project_info$gene, '_', filter_name, '_filtered_variants'))
                )
              ),
              rownames = FALSE,
              class = "cell-border stripe hover"
            )
          
          if ("IMPACT_annotation" %in% available_cols) {
            dt_table <- dt_table %>%
              formatStyle("IMPACT_annotation", backgroundColor = styleEqual(c("HIGH", "MODERATE", "LOW", "MODIFIER"), c("#ffcccc", "#ffffcc", "#ccffcc", "#e6e6e6")))
          }
          
          print(htmltools::tagList(dt_table))
          
          cat('\n\n**_Table ', 2 + length(custom_filter_names) + match(filter_name, custom_filter_names), ':_** *Interactive table of variants that passed ', filter_display, ' for {{GENE_NAME}}. Use the search and filter features to explore specific variants.*\n\n', sep = "")
        } else {
          cat("\nNo", filter_display, "filtered variants available.\n\n")
        }
      }, error = function(e) {
        cat("\nCould not load", filter_display, "filtered variants data.\n\n")
      })
    } else {
      cat("\nNo filtered variants table found for ", filter_display, ".\n\n", sep = "")
    }
    
    cat('\n---\n\n')
  }
} else {
  cat("No custom filtering has been applied to this gene dataset.\n\n")
}
```


---

# Report Information

**Pipeline Details:**  
- **Project Code**: {{PROJECT_CODE}}  
- **Project Name**: {{PROJECT_NAME}}  
- **Gene Analyzed**: {{GENE_NAME}}  
- **Report Type**: Small Variants Quality Control  
- **Analysis Author**: {{PROJECT_AUTHOR}}  
- **Report Format**: HTML (Self-contained)  
- **Generation Date**: `r Sys.Date()`  
- **R Version**: `r R.version.string`  

---

*This report was generated automatically by the {{PROJECT_CODE}} Nextflow pipeline using Quarto.*  
*For questions about the analysis or interpretations, please contact the project team.*